Progress Report

### 2023-09-26 Docs/ProgressReport.Rmd
format

df %>% 
  filter(SEQN %in% rand_id) %>%
  ggplot()+
  geom_point(aes(x=sind, y=Z), size = 0.5)+
  facet_wrap(~SEQN)+
  labs(x="Time", y = "Activity", title = "A brief overview of the outcome")
```
## fGFPCA

@@

### Out-of-sample prediction

@@

- $s$: bin index
- $t_{m_s}$: midpoint time of bin s
- $\mathcal{T}_s$: all observation points in bin s
- $Y_i^s)$ all observations in bin s from subject i

@@

data.frame(bin = mid, eta_pred = eta_pred_out) %>% 
  right_join(df %>% filter(id==rand_id) %>%  select(Y, sind, bin), by = "bin") %>%
  ggplot()+
  geom_point(aes(x=sind, y = Y))+
  geom_line(aes(x=sind, y = exp(eta_pred)/1+exp(eta_pred)))+
  labs(title = rand_id)

@@

## Full data application output

### fGFPCA

>>>>

df %>% 
  filter(SEQN %in% rand_id) %>%
  ggplot()+
  geom_point(aes(x=sind, y=Z), size = 0.5)+
  facet_wrap(~SEQN)+
  labs(x="Time", y = "Activity", title = "A brief overview of the outcome")
```
## fGFPCA model fitting

@@

## Out-of-sample prediction

@@

- $s$: bin index
- $t_{m_s}$: midpoint time of bin s
- $\mathscr{T}_s$: all observation points in bin s
- $Y_i^s$ all observations in bin s from subject i

@@

data.frame(bin = mid, eta_pred = eta_pred_out) %>% 
  right_join(df %>% filter(id==rand_id) %>%  select(Y, sind, bin), by = "bin") %>%
  ggplot()+
  geom_point(aes(x=sind, y = Y))+
  geom_line(aes(x=sind, y = exp(eta_pred)/(1+exp(eta_pred))))+
  labs(title = rand_id)

@@

# Full data application output

## fGFPCA
